---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# EMK

EMK is a collection of miscellaneous functions I have written that I personally find helpful in a variety of contexts.

## Installation

You can install EMK from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("EllaKaye/EMK")
```

```{r}
library(EMK)
```


## `n_letter_words`
`n_letter_words` is a function that will produce all 'words' of `n` letters long. Its usage is `n_letter_words(n, num_letters = 26, case = c("upper", "lower"), as_vector = FALSE)`.

```{r n_letter_word_example}
n_letter_words(3)
three_vec <- n_letter_words(3, as_vector = TRUE)
c(head(three_vec), tail(three_vec))
n_letter_words(5, num_letters = 2, case = "lower")
```

## `ggpres`
Typically, if you have a plot designed to look good in print, when it is included in a presentation, the text on the title, axes, legend and facet strips is too small to be read by everyone in the room. `ggpres` fixes that by taking a `ggplot` plot and increasing the size of the text. Usage is `ggpres(g, title_size = 24, text_size = 18)`.

```{r ggpres_example, out.width="100%"}
library(ggplot2)
g <- ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(~class, scales = "free") + 
   ggtitle("A faceted plot")
g
ggpres(g, text_size = 16)
```

